---
title: "MA615_Berries_Kunyu Liu"
author: "Kunyu Liu"
date: "10/15/2020"
output:
  pdf_document: 
    latex_engine: xelatex
    keep_tex: yes
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,out.width="0.9\\linewidth",dev="pdf",fig.align  = 'center')
pacman::p_load(
  "tidyverse"
)

knitr::include_graphics
```

***

# Introduction
The berries data were collected from the USDA database and stored online[^1], which contains blueberries, raspberries, and strawberries. 
***
# Data Cleaning

## Data Import

```{r}
berries = read.csv('berries.csv', header = TRUE)
im1 = berries %>%
  select(Year,Period,State,Commodity,Data.Item,Domain,Domain.Category,Value)
head(im1)
```
## Initial Screening of the Data

There are many categorical variables, we need to replace many (D),(NA),(X) and (Z) with NA in Value, because this column is defined as categorical. 

```{r}
im1$Value <- as.numeric(im1$Value)
# Replace (D),(NA),(X) and (Z) with NA
im1[im1 =="(D)"] = NA
im1[im1 =="(NA)"] = NA
im1[im1 =="(X)"] = NA
im1[im1 =="(Z)"] = NA

# summary the new dataset
summary(im1)
```

## Further data cleaning on strawberries

### Cleaning - `Data Item`
Use `filter` function for extracting data of strawberries

```{r}
im2 = im1 %>% filter(Commodity=="STRAWBERRIES")
summary(im2)

strawberry1 = im2 %>% drop_na()

pre = strawberry1$Data.Item
m1 = gsub(" - ",",",pre)

unit1 = str_extract_all(m1, "MEASURED.*[^./AVG]|ACRES")
unit1 = str_replace(unit1, ",","")
unit1 = trimws(1)
```
```{r}
type1 = str_extract_all(m1,"(FRESHMARKET)|(PROCESSING)")
type_data = data.frame(Market.Channel=as.character(type1))
type_data[type_data=="character(0)"] = NA
```

***
# EDA
## Data exploration
### Summarize Data
Because the measurement of each data are different, we need to group and summarize them.
```{r warning=FALSE}
# Measurement of the strawberry
strawberry1$unit = str_extract_all(m1,"MEASURED IN.*[^, /AVG]|ACRES.*")
strawberry1$unit = as.character(strawberry1$unit)
sum1 = strawberry1 %>%
  group_by(unit)%>%
  summarize(
    count=n(),
    value=sum(Value)
    )
```

### Plot the whole dataset
```{r}
a1 = ggplot(data = sum1, mapping = aes(x = unit, y = count))+
   geom_point()
print(a1)
a2 = ggplot(data = sum1, mapping = aes(x = unit, y = value, size = count)) +
  geom_point(shape=21, alpha = 0.5) 
print(a2)
```
From the first plot, we can see the number of each measurement. The second plot shows the reason for seperate variable item.

## Further EDA
### Creat a new frame in order to exact data to do the further EDA

```{r}
unit_new = strawberry1 %>%
  group_by(unit)%>%
  summarize(
    state=State,
    year= Year,
    count=n(),
    value=Value
    )

tail(unit_new)
```
```{r}
# Do a plot, excluding outliers
boxplot = ggplot(unit_new, aes(x = unit, y = value))+ 
  geom_boxplot(outlier.colour = NA,notch = TRUE) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1),
        axis.text = element_text(size = 7),
        axis.title = element_text(size = 13, face = "bold")) +
  coord_cartesian(ylim = c(0, 1000)) 
print(boxplot)
```
### Creat a data frame contain MEASURED IN LB

```{r}
LB = filter(unit_new,unit=="MEASURED IN LB" )
LB$value = as.numeric(LB$value)
LB$value[LB$value ==0] = NA
LB_new = group_by(LB,year,state)
LB_final = summarize(LB_new, value = mean(value, na.rm = TRUE))
summary(LB_final)

# Making plot
a3 = ggplot(LB_final, aes(x = year, y = value))+
  geom_point(aes(color=state))
print(a3)
```
From the plot above, we can see that California always has the highest value in each year when we measured in LB, except in year 2016.

### Making boxplot of MEASURED IN LB
```{r}
# excluding outliers
bp1 = ggplot(LB_final, aes(x = year, y = value))
bp1 = bp1 + geom_boxplot(outlier.colour = NA) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1),
        axis.text = element_text(size = 11),
        axis.title = element_text(size = 13, face = "bold")) +
  coord_cartesian(ylim = c(200, 1000)) +
  labs(x = "LB_final")
print(bp1)
```
From the boxplot, we can find the value for LB_final is between 400-700

### Creat a data frame contain MEASURED IN  $ / CWT
```{r}

CWT = filter(unit_new,unit=="MEASURED IN $ / CWT" )
CWT$value = as.numeric(CWT$value)
CWT$value[CWT$value ==0] = NA
CWT_new = group_by(CWT,year,state)
CWT_final = summarize(CWT_new, value = mean(value, na.rm = TRUE))
summary(CWT_final)

# Making plot
a4 = ggplot(CWT_final, aes(x = year, y = value))+
  geom_point(aes(color=state))
print(a4)
```
From the plot above, we can see that New York has the highest value in each year when we measured in $ / CWT.

### Making boxplot of MEASURED IN  $ / CWT
```{r}
# excluding outliers
bp2 = ggplot(CWT_final, aes(x = year, y = value))
bp2 = bp2 + geom_boxplot(outlier.colour = NA) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1),
        axis.text = element_text(size = 11),
        axis.title = element_text(size = 13, face = "bold")) +
  coord_cartesian(ylim = c(0, 300)) +
  labs(x = "CWT_final")
print(bp2)
```
From the boxplot, we can find the value for CWT_final is between 100-200

***
# Discussion
From the analysis we did above, we can conclude that the California is a good state for buying strawberry, but further analysis is needed in better determine this conclusion, because some states have missing values for some variables. Thus, we need further analysis to find out all the states have the same measurement.

***

# References

(^1): Berry Dataset(https://quickstats.nass.usda.gov/results/D416E96E-3D5C-324C-9334-1D38DF88FFF1)

Guided by Chenghao Meng & Yuxin Wang




